\begin{abstract}Hardware virtualization has been gaining a significant share of computing timein the last years. Using virtual machines (VMs) for parallel computing is anattractive option for many users. A VM gives users a freedom of choosing anoperating system, software stack and security policies, leaving the physicalhardware, OS management, and billing to physical cluster administrators. Thewell-known solutions for cloud computing, both commercial (Amazon Cloud, GoogleCloud, Yahoo Cloud, etc.) and open-source (OpenStack, Eucalyptus) provideplatforms for running a single VM or a group of VMs. With all the benefits,there are also some drawbacks, which include reduced performance when runningcode inside of a VM, increased complexity of cluster management, as well as theneed to learn new tools and protocols to manage the clusters.At SDSC, we have created a novel framework and infrastructure by providing virtualHPC clusters to projects using the NSF sponsored {\em Comet} supercomputer.Managing virtual clusters on {\em Comet} is similar to managing a bare-metal cluster in terms of processes and tools that are employed. This is beneficial becausesuch processes and tools are familiar to cluster administrators. Unlikeplatforms like AWS, {\em Comet}'s virtualization capability supportsinstalling VMs from ISOs (i.e., a CD-ROM or DVD image) or via an isolatedmanagement VLAN (PXE). At the same time, we're helping projects take advantageof VMs by providing an enhanced client tool for interaction with our managementsystem called Cloudmesh client. Cloudmesh client can also be used to managevirtual machines on OpenStack, AWS, and Azure.The article describes our design and approach to running virtual clusters, thetools we developed, and initial user experience.\end{abstract}